### 2012-11-15 doc/progress_plan/report.tex
Talking about research papers and sources

>>>>

The most convenient and accessible source is the ART corpus that SAPIENTA was
trained with\cite{citeulike:11077287}. This corpus is already stored using the
CoreSC schema and has been pre-annotated. This means that Partridge would not
need to do any conversion or pre-processing on the papers. These scientific
papers are all chemistry papers. Therefore, more papers from other scientific
domains are needed to get a wider variety of topics and make Partridge useful
to as wide an audience as possible.
